\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2023-11-07 doc/USER_MANUAL/05_running_the_solver.tex
- minor edit of the 'reuse' feature description.

In addition to inbuild source-time functions, the solver can also use an external source-time function defined by the user. This option can be activated by setting \texttt{USE\_EXTERNAL\_SOURCE\_FILE} to \texttt{.true.} in \texttt{DATA/Par\_file} and by adding the name of the file containing the source-time function at the end of \texttt{FORCESOLUTION} or \texttt{CMTSOLUTION} files.
The source-time function file must contain a single column with the amplitudes of the source-time function for all the time steps. The time step must be exactly the same as that used for the simulation. When the flag is set to \texttt{.false.}, then the line with the external source-time function file must not appear in the files \texttt{FORCESOLUTION} and \texttt{CMTSOLUTION}, otherwise the solver will exit with an error. When using an external source file, you can still set up the source location and directivity as in the default case.
In the \texttt{FORCESOLUTION} file: you set "latorUTM", "longorUTM" and "depth" to define the position of your point source. Then if you want to define a directivity, change the following lines: "component dir vect source E", "component dir vect source N" and "component dir vect source Z\_UP". What you are doing is simply that you define the source position and directivity the same way as in the default case, but in addition you are specifying the path to read in a non-default source-time function from an external file.

>>>>

In addition to inbuild source-time functions, the solver can also use an external source-time function defined by the user. This option can be activated by setting \texttt{USE\_EXTERNAL\_SOURCE\_FILE} to \texttt{.true.} in \texttt{DATA/Par\_file} and by adding the name of the file containing the source-time function at the end of \texttt{FORCESOLUTION} or \texttt{CMTSOLUTION} files.
The source-time function file must contain a single column with the amplitudes of the source-time function for all the time steps. The time step must be exactly the same as that used for the simulation. If the external source-time functions are same for all the sources, differing only in their respective time shift, you can define the source-time function file only for the first source and set the external source-time function file to 'reuse' and define the appropriate value of \texttt{time shift} for all the other sources. When the flag is set to \texttt{.false.}, then the line with the external source-time function file must not appear in the files \texttt{FORCESOLUTION} and \texttt{CMTSOLUTION}, otherwise the solver will exit with an error. When using an external source file, you can still set up the source location and directivity as in the default case.
In the \texttt{FORCESOLUTION} file: you set "latorUTM", "longorUTM" and "depth" to define the position of your point source. Then if you want to define a directivity, change the following lines: "component dir vect source E", "component dir vect source N" and "component dir vect source Z\_UP". What you are doing is simply that you define the source position and directivity the same way as in the default case, but in addition you are specifying the path to read in a non-default source-time function from an external file.
